\documentclass[a4paper]{article}
\usepackage[slantfont, boldfont, CJKtextspaces, CJKmathspaces]{xeCJK}
\usepackage{fontspec,xunicode,xltxtra}
\usepackage[pagestyles]{titlesec}
\usepackage{indentfirst}
\usepackage[top=1in,bottom=1in,left=1.25in,right=1.25in]{geometry}
\usepackage{amsmath}
\usepackage[usenames,dvipsnames]{color}
%\usepackage[colorlinks,linkcolor=red,anchorcolor=Blue,citecolor=green]{hyperref}

\setCJKmainfont[BoldFont={黑体}, ItalicFont={楷体_GB2312}]{宋体}
\setmainfont{Liberation Serif} 
\setsansfont{Liberation Sans} 
\setmonofont{文泉驿等宽微米黑}

\punctstyle{kaiming} % 开明式标点格式  

\titleformat{\section}{\Large\bfseries}{\S\,\thesection}{1em}{}
\titleformat{\subsection}{\large\bfseries}{\S\,\thesubsection}{1em}{}
\newpagestyle{main}{
	\sethead{\small\S\,\thesection\quad\sectiontitle}{}{$\cdot$~\thepage~$\cdot$}
	\setfoot{}{}{}\headrule
}
\renewcommand{\contentsname}{目录Content}
\renewcommand{\abstractname}{摘要Abstract}
%\renewcommand{\today}{\number\year 年 \number\month 月}
\renewcommand\refname{参考文献References}

\pagestyle{main}
\date{2011-08-30}

\begin{document}

\title{利用图论模型解决几类特殊的线性规划问题 \\
METHODS BASED ON GRAPH MODELS TO SOLVE SPECIAL KINDS OF LINEAR PROGRAMMING}
\author{高2013级13班 李凌霄 \\
Class 13, Grade 2013, Lingxiao Li}
\maketitle
\begin{abstract}
	线性规划(Linear Programming，简称LP)是最优化问题中的重要领域之一，
	研究线性约束下线性目标函数的最值问题，
	广泛应用于军事作战、经济分析、经营管理和工程技术等方面。\par
	本文提出了几类特殊的线性规划问题，通过与图论模型相联结，
	得到了较好的解决。
	\par
	\vspace{0.6cm}
	Linear Programming is a mathematical method for determining a way
	to achieve the best outcome in a given mathematical model for some 
	list of requirements represented as linear relationships, 
	which has proved useful in modeling diverse types of problems in 
	planning, routing, scheduling, assignment, and design.\par
	This thesis suggests several kinds of LP problems with speciality
	which can be solved with analogy to classic graph models, 
	such as shortest path, weighted perfect matching, and network flow.
\end{abstract}
\tableofcontents


\input{sec1}
\input{sec2}
\input{sec3}

\section{总结}
一些看似与图论无关的问题，在合理的数学抽象之后，通过类比，
成功地转化为了可解决的图论模型。整个过程看似天马行空，
实际上只不过是几个简单问题的组合。在这其中，
起着串联作用的就是类比思想。这如同一位大牛所说：“养成主动类比的习惯是非常有效的，尤其在山穷水尽之时，其往往能够让我们柳暗花明！当然，类比思维建立在\textbf{非常扎实的基础算法功底}之上。”

\input{bib}

\end{document}
